---
title: "Homework 0"
author: "Elizabeth Imhoff"
format: html
editor: visual
execute: 
  echo: FALSE
---

1.  

```{r}
a <- 1
b <- 3
c <- 2

sol <- (-b + sqrt(b^2 - 4*a*c))/2*a
sol_2 <- (-b - sqrt(b^2 - 4*a*c))/2*a

if (is.numeric(sol) == TRUE & is.numeric(sol_2) == TRUE){
  print(sol)
  print(sol_2)

} else if (is.numeric(sol) == FALSE & is.numeric(sol_2) == TRUE){
  print(sol_2)
} else if (is.numeric(sol) == TRUE & is.numeric(sol_2) == FALSE){
  print(sol)
  
} else {print("None")}

```

Above are the solution(s) to the quadratic equation.

2.  

```{r}
x <- seq(-5,5,0.1)
plot(x, a*x^2 + b*x + c, type = "l")
abline(h=0, lty = 2)
```

This plot is the graph of quadratic function. When a=1, b=3, and c=2, the solutions to the quadratic equation are -2 and -1, which are where the function crosses the x-axis. If the function (plotted line) did not cross the x-axis, then the there would be no solutions to the equation. If the function crosses the x-axis once, then there is only one solution to the quadratic equation.
